Efficient N-Dimensional surface estimation using Crofton formula and run-length encoding

### 2012-01-25 article/Article.tex
eqn equivalent perimeter
ajoute equations et refs

The roundness is defined the ratio of equivalent $d$-perimeter over the measured $d$-perimeter:
\begin{eqnarray}
roundness = \frac{P_{eq}}{P}
\end{eqnarray}

@@

Planar test shapes include:
\begin{itemize}
\item disks
\item ring, obtained by the difference of several disks
\item trefoil shape
\item ellipses with $a=XX$ and $b=XX$
\item rectangle with length $XX$ and width $XX$
\end{itemize}

 % Example of reconstruction of a discrete disk
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=5cm]{images/discreteDisk}
\end{center}
\end{figure}

Test shapes for 3D measurements include:
\begin{itemize}
\item balls with various radii
\item hollow ball
\item prolate and oblate ellipsoids
\item cuboids
\end{itemize}

@@

where the $d$-uple $(\Delta_{1},\ldots,\Delta_{d})$ defines the pixel
or voxel size. A digitization scheme represents how a continuous
structure $X$ is digitized into a binary image $X_\text{d}$. According to
the lattice scheme, $X_\text{d} = X\cap\mathbb{L}^d$. According to the
covering scheme a grid point $x$ belongs to $X_\text{d}$ if the grid
cell centered on $x$ hits $X$. 
This paper assumes isotropic resolution, i.e. $\Delta_{i}$ being the same for all $i$.

>>>>

The roundness is defined the ratio of equivalent $d$-perimeter over the measured $d$-perimeter. 
The equivalent $d$-perimeter is defined as the perimeter of the $d$-ball with same volume $V$.
\begin{eqnarray}
roundness             & = & \frac{P_{eq}}{P} \\
P_{eq}                & = & \frac{d \cdot V_{eq}}{R_{eq}} \\
R_{eq}                & = & \sqrt[\displaystyle d]{\frac{V\cdot\Gamma(\frac{d+1}{2})}{\pi^\frac{d}{2}}} \\
\Gamma(\frac{d+1}{2}) & = & \begin{cases}
                               \displaystyle \frac{d}{2}!  &\text{if}~ d ~\text{is even} \\
                               \displaystyle \frac{\sqrt{\pi} \cdot d!!}{2^{\frac{d+1}{2}}}  &\text{if}~ d ~\text{is odd} \\
                            \end{cases} \\
d!!                   & = & \begin{cases}
                                1 &\text{if}~ d \leq 1 \\
                                d \cdot (d-2)!!  & \text{otherwise} \\
                             \end{cases}
\end{eqnarray}

@@

Planar test shapes include disks, rings obtained by the difference of several disks,
trefoil shape, ellipses with $a=XX$ and $b=XX$, and rectangle with length $XX$ and width $XX$.

Test shapes for 3D measurements include
balls with various radii, hollow ball, prolate and oblate ellipsoids, and cuboids. 
For each type of shape, several orientations were considered.

@@

where the $d$-uple $(\Delta_{1},\ldots,\Delta_{d})$ defines the pixel
or voxel size. A digitization scheme represents how a continuous
structure $X$ is digitized into a binary image $X_\text{d}$. 
According to the
covering scheme a grid point $x$ belongs to $X_\text{d}$ if the grid
cell centered on $x$ hits $X$ (See Fig.~\ref{fig:DiskDiscretization}).

% Example of reconstruction of a discrete disk
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=5cm]{images/discreteDisk}
\end{center}
\caption{Discretization of a disk}
\label{fig:DiskDiscretization}
\end{figure}
This paper assumes isotropic resolution, i.e. $\Delta_{i}$ being the same for all $i$.
